Titeln på avhandlingens språk

### 2023-05-19 body/part1/chapter2-relatedwork/key_contributions.tex
cleaning up for publication

\section{Overview of our contributions}\label{sec:contributions}

\begin{figure}
    \centering
    \begin{forest}
        for tree={% style of tree
            align=center,
            grow=0,reversed, % tree direction
            parent anchor=east,
            child anchor=west, % edge anchors
            edge={line cap=round},
            outer sep=+1pt, % edge/node connection
            rounded corners,minimum width=15mm,minimum height=8mm, % node shape
            l sep=7mm % level distance
        }
        [{\scshape Contributions}
            [Methodology
                [{Use-case\\studies} [\acs{WCA}] [\acsp{NCS}]]
                [{Tooling} [{EdgeDroid\\(\acs{WCA})}] [{\acs{CLEAVE}\\(\acsp{NCS})}] [Ainur\\(testbed)]]
            ]
            [{Implications of\\Accuracy in\\the Emulation}
                [{Characterization of\\human behavior in \acs{WCA}}]
                [{Realistic human\\model for \acs{WCA}}]
                [Exploration of avenues\\for optimization of \acs{WCA}]
            ]
        ]
        \end{forest}
    \caption{Hierarchical overview of the main and secondary contributions of this dissertation.}\label{fig:contribs}
\end{figure}

This thesis presents two key contributions and a number of sub-contributions to literature, as illustrated in \cref{fig:contribs}.
Firstly, we introduce a methodology for the performance evaluation of latency-sensitive, feedback-loop-based applications enabled by Edge Computing such as \gls{MAR} and \glspl{CPS}.
This methodology is validated by example through two representative use-cases, and we provide tooling for its implementation.
Secondly, we study the implications improved client-side emulation accuracy has on the results produced with our methodology.
These implications are again explored by example.
We design and implement of a detailed model of human user behavior in \gls{WCA}, and then use it to study the potential for optimization of these systems.

@@

Our first contribution corresponds to a methodological approach to the study and performance evaluation of Edge-enabled latency-sensitive applications. 
This approach is based on the novel idea of emulating \emph{only} the end-user component of such applications while using the \emph{real} network and compute components of the system.
In other words, our methodology involves replacing the client side of the system with commercial off-the-shelf (COTS) general-purpose computing devices running realistic software imitations of the desired behaviors, while retaining the real network and compute hardware at the backend.
This entails modeling and emulating human inputs in \gls{MAR} applications and the physical components of \glspl{CPS}.

We study and validate our methodology by example, investigating its applicability in two representative use-cases for \gls{XR} applications and \glspl{CPS}, respectively: \acf{WCA} and \acfp{NCS}.
\cref{paper:olguinmunoz2018demoscaling,paper:olguinmunoz2019edgedroid} discuss initial explorative studies into the application of our methodology for \gls{WCA}.
These works present the first empirical results obtained with our methodological approach, providing thus an initial validation of its utility for research, and further discuss the necessary tooling and software frameworks required for the implementation of our methodology.
In particular, we introduce in these works a trace-based emulation tool which we call EdgeDroid.
It uses a trace of inputs recorded in optimal conditions, the replay of which is controlled at run-time by a simple model of human behavior based on a \gls{FSM}.

\Cref{paper:olguinmunoz2022cleave} extends our methodology to the study of control systems for \glspl{NCS} on Edge Computing.
These applications are similarly difficult to benchmark as \gls{WCA}, particularly at scale on multi-tenant systems, due to their client-side complexity and extreme sensitivity to latency.
To address these challenges, we introduce yet another tool, \gls{CLEAVE}, for the emulation and subsequent deployment of these systems on edge computing infrastructure.
\gls{CLEAVE} allows us both to emulate the physical components of a relatively simple control system plant and deploy real algorithms for its control.
The middleware software abstracts away the network from the development of these workloads, enabling quick prototyping and deployment.
We then present use-case scenarios demonstrating the scalability and flexibility of their approach by deploying scenarios with a large number of loops without the need for domain-specific hardware.

In \cref{paper:olguinmunoz2022ainur} we also briefly discuss Edge Computing testbed research and automation as an ancillary contribution to the methodology.
This paper formally introduces the Ainur framework for Edge Computing testbed automation and workload orchestration.
This framework is employed in \cref{paper:olguinmunoz2023realistic,paper:olguinmunoz2022cleave} for the orchestration of the Edge Computing testbeds on which the developed tools were deployed.
Ainur represents an ancillary contribution, crucial for the research presented in these works.
Without it, the experimental approach described in these works would not have been feasible.

We argue that our approach presents several advantages over existing methods for the study of trade-offs in latency-sensitive applications.
Our methodology allows for efficient and repeatable evaluation of Edge environments while avoiding many of the complications associated with experimental evaluation.
Emulating the workload component reduces complexity by moving it into the software domain, allowing for easier horizontal scaling through the use of \gls{COTS} general-purpose hardware such as \glspl{SBC}.
This also reduces the barrier of entry to  research, as \glspl{SBC} are for the most part cheap and easily accessible, and further preserves the realism of effects stemming from the hardware and network.
In particular, the methodology allows us to capture effects due to network factors such as contention, congestion control, and medium access, which are often of stochastic or chaotic natures and complex to capture in simulations.
The softwarized nature of the client-side emulation allows for straightforward automation through general-purpose programming and scripting languages.
Repeatability and replicability are also enhanced, as repeating a study becomes a matter of re-running the workload on the same testbed, and studies can be replicated simply by obtaining the same or equivalent software workload and deploying it on a comparable testbed.
These are complex tasks to accomplish in real-world approaches, particularly when dealing with humans.

@@

The second key contribution of this dissertation relates to the exploration of the question of what degree of detail about the physical world must be captured by a client-side emulation of a latency-sensitive, feedback-loop application on Edge Computing.
We explore this interrogative through the elaboration of a detailed model of human user behavior in \gls{WCA}, which we then combine with mathematical framework to study the potential for optimization of these applications.

\cref{paper:olguinmunoz2021impact} begins this work by presenting a characterization of human behavior in \gls{WCA}, developed through a human subject study in which participants interact with an instrumented application.
System responsiveness was altered in real-time during each execution of the task, and we recorded participants' reactions by measuring task- and system-related metrics, as well as biometrics from sensors placed on their bodies.
Participants were also asked to fill out two personality indicator questionnaires, allowing us to later correlate individual personality traits and measured reaction to changes in system responsiveness.

Next, in \cref{paper:olguinmunoz2023realistic} we introduce the first ever data-driven model of human timings for \gls{WCA}, built upon the data and insights collected for \cref{paper:olguinmunoz2021impact}.
The model is validated against previously obtained results, both through simulated, controlled executions and deployments on a real edge computing testbed.
The paper goes on to explore potential implications of this model for \gls{WCA} system optimization potential, particularly in the domains of energy consumption and sampling strategies.

We conclude that realistic, dynamic human behavior in the client-side emulation enables superior optimization approaches that would otherwise be inviable to implement.
The findings from this research highlight that simply focusing on system-related metrics or performance optimizations may not be sufficient, as human behavior and reactions play a critical role in the overall performance of such applications.
By considering human behavior as an integral part of the emulation process, we demonstrate that it is possible to develop more realistic and effective optimization approaches that take into account the intricacies of human-computer interaction.
These findings have significant implications for the design and optimization of \gls{WCA} applications, particularly in the areas of energy consumption, sampling strategies, and application lifetime.

>>>>

\section{Overview of the contributions of this dissertation}\label{sec:contributions}

\begin{figure}
    \centering
    \begin{forest}
        for tree={% style of tree
            align=center,
            grow=0,reversed, % tree direction
            parent anchor=east,
            child anchor=west, % edge anchors
            edge={line cap=round},
            outer sep=+1pt, % edge/node connection
            rounded corners,minimum width=15mm,minimum height=8mm, % node shape
            l sep=7mm % level distance
        }
        [{\scshape Contributions}
            [Methodology
                [{Use-case\\studies} [\acs{WCA}] [\acsp{NCS}]]
                [{Tooling} [{EdgeDroid\\(\acs{WCA})}] [{\acs{CLEAVE}\\(\acsp{NCS})}] [Ainur\\(testbed)]]
            ]
            [{Implications of\\accuracy in\\the emulation}
                [{Characterization of\\human behavior in \acs{WCA}}]
                [{Realistic human\\model for \acs{WCA}}]
                [Exploration of avenues\\for optimization of \acs{WCA}]
            ]
        ]
        \end{forest}
    \caption{Hierarchical overview of the main and secondary contributions of this dissertation.}\label{fig:contribs}
\end{figure}

This thesis presents two key contributions and a number of sub-contributions to literature, as illustrated in \cref{fig:contribs}.
Firstly, I introduce a methodology for the performance evaluation of latency-sensitive, feedback-loop-based applications enabled by Edge Computing such as \gls{MAR} and \glspl{CPS}.
This methodology is validated by example through two representative use-cases, and I provide tooling for its implementation.
Secondly, I study the implications improved client-side emulation accuracy has on the results produced with our methodology.
These implications are again explored by example.
I design and implement of a detailed model of human user behavior in \gls{WCA}, and then use it to study the potential for optimization of these systems.

@@

My first contribution corresponds to a methodological approach to the study and performance evaluation of Edge-enabled latency-sensitive applications. 
This approach is based on the novel idea of emulating \emph{only} the end-user component of such applications while using the \emph{real} network and compute components of the system.
The methodology involves replacing the client side of the system with \gls{COTS}, general-purpose computing devices running realistic software imitations of the desired behaviors, while retaining the real network and compute hardware at the backend.
This entails modeling and emulating human inputs in \gls{MAR} applications and the physical components of \glspl{CPS}.

I study and validate this methodology by example, investigating its applicability in two representative use-cases for \gls{XR} applications and \glspl{CPS}, respectively: \acf{WCA} and \acfp{NCS}.
\cref{paper:olguinmunoz2018demoscaling,paper:olguinmunoz2019edgedroid} discuss initial explorative studies into the application of the methodology for \gls{WCA}.
These works present the first empirical results obtained with my methodological approach, providing an initial validation of its utility for research.
Further, I discuss the necessary tooling and software frameworks required for the implementation of my methodology.
In particular, my co-authors and I introduce in these works a trace-based emulation tool which we call EdgeDroid.
It uses a trace of inputs recorded in optimal conditions, the replay of which is controlled at run-time by a simple model of human behavior based on a \gls{FSM}.

\Cref{paper:olguinmunoz2022cleave} extends my methodology to the study of control systems for \glspl{NCS} on Edge Computing.
These applications are similarly difficult to benchmark as \gls{WCA}, particularly at scale on multi-tenant systems, due to their client-side complexity and extreme sensitivity to latency.
To address these challenges, my co-authors and I introduce yet another tool, \gls{CLEAVE}, for the emulation and subsequent deployment of these systems on edge computing infrastructure.
\gls{CLEAVE} allows us both to emulate the physical components of a relatively simple control system plant and deploy real algorithms for its control.
The middleware software abstracts away the network from the development of these workloads, enabling quick prototyping and deployment.
We then present use-case scenarios demonstrating the scalability and flexibility of their approach by deploying scenarios with a large number of loops without the need for domain-specific hardware.

In \cref{paper:olguinmunoz2022ainur}, we also briefly discuss Edge Computing testbed research and automation as an ancillary contribution to the methodology.
This paper formally introduces the Ainur framework for Edge Computing testbed automation and workload orchestration.
This framework is employed in \cref{paper:olguinmunoz2023realistic,paper:olguinmunoz2022cleave} for the orchestration of the Edge Computing testbeds on which the developed tools were deployed.
Ainur represents an ancillary contribution, crucial for the research presented in these works.
Without it, the experimental approach described in these works would not have been feasible.

I argue that my approach presents several advantages over existing methods for the study of trade-offs in latency-sensitive applications.
The methodology allows for efficient and repeatable evaluation of Edge environments while avoiding many of the complications associated with experimental evaluation.
Emulating the workload component reduces complexity by moving it into the software domain, allowing for easier horizontal scaling through the use of \gls{COTS} general-purpose hardware such as \glspl{SBC}.
This also reduces the barrier of entry to  research, as \glspl{SBC} are for the most part cheap and easily accessible, and further preserves the realism of effects stemming from the hardware and network.
In particular, the methodology allows for the capture of effects due to network factors such as contention, congestion control, and medium access, which are often of stochastic or chaotic natures and complex to capture in simulations.
The softwarized nature of the client-side emulation allows for straightforward automation through general-purpose programming and scripting languages.
Repeatability and replicability are also enhanced, as repeating a study becomes a matter of re-running the workload on the same testbed, and studies can be replicated simply by obtaining the same or equivalent software workload and deploying it on a comparable testbed.
These are complex tasks to accomplish in real-world approaches, particularly when dealing with humans.

@@

The second key contribution of this dissertation relates to the exploration of the question of what degree of detail about the physical world must be captured by a client-side emulation of a latency-sensitive, feedback-loop application on Edge Computing.
I explore this interrogative through the elaboration of a detailed model of human user behavior in \gls{WCA}, which I then combine with mathematical framework to study the potential for optimization of these applications.

\cref{paper:olguinmunoz2021impact} begins this work by presenting a characterization of human behavior in \gls{WCA}, developed through a human subject study in which participants interact with an instrumented application.
System responsiveness is altered in real-time during each execution of the task, and we record participants' reactions by measuring task- and system-related metrics, as well as biometrics from sensors placed on their bodies.
Participants are also asked to fill out two personality indicator questionnaires, allowing to later correlate individual personality traits and measured reaction to changes in system responsiveness.

Next, in \cref{paper:olguinmunoz2023realistic} my co-authors and I introduce the first ever data-driven model of human timings for \gls{WCA}, built upon the data and insights collected for \cref{paper:olguinmunoz2021impact}.
The model is validated against previously obtained results, both through simulated, controlled executions and deployments on a real edge computing testbed.
The paper goes on to explore potential implications of this model for \gls{WCA} system optimization potential, particularly in the domains of energy consumption and sampling strategies.

I conclude that realistic, dynamic human behavior in the client-side emulation enables superior optimization approaches that would otherwise be inviable to implement.
The findings from this research highlight that simply focusing on system-related metrics or performance optimizations may not be sufficient, as human behavior and reactions play a critical role in the overall performance of such applications.
By considering human behavior as an integral part of the emulation process, I demonstrate that it is possible to develop more realistic and effective optimization approaches that take into account the intricacies of human-computer interaction.
These findings have significant implications for the design and optimization of \gls{WCA} applications, particularly in the areas of energy consumption, sampling strategies, and application lifetime.

### 2023-05-19 body/part1/chapter2-relatedwork/relatedwork.tex
cleaning up for publication

Nevertheless, a small body of works has attempted to tackle this challenge through analytical approaches.
Examples include~\cite{chen2015efficient,champati2015one,champati2016semi,al2017reliable}.
In~\cite{chen2015efficient}, the authors formulate the problem of computation offloading in \gls{MEC} as a multi-user computation offloading game, and design a distributed computation offloading algorithm that achieves a Nash equilibrium to solve it.
They demonstrate through numerical results that the proposed algorithm achieves good computation offloading performance and has good scaling capabilities.
Another work that tackles computation offloading is~\cite{champati2015one}, in which the authors propose a novel optimization algorithm for the cost optimization of hybrid clouds.
The algorithm selects tasks for remote computation on the public cloud based on their estimated processing times and the known cost of offloading them; tasks with large processing times that offset their offloading cost are offloaded.\@
\cite{champati2016semi} proposes semi-online algorithms to to minimize the time required to complete all computational tasks in a sequence, with communication delay, in Cloud Computing environments.
This is achieved by optimizing the scheduling of independent tasks with unknown processing times.
Finally, the authors of~\cite{al2017reliable} propose a model-based rate adaptation algorithm for scalable video streaming in multihop wireless networks.
The algorithm is built on a novel performance model based on stochastic network calculus and allows fast near-optimal rate adaptation for fixed transmission paths and cross-layer optimized routing.

@@

Approaches to performance evaluation of distributed systems using simulations also exist in literature, particularly geared towards the Cloud~\cite{mansouri2020cloud}.
Examples of such approaches include the \emph{CloudSim}, \emph{iCanCloud}, and \emph{GreenCloud} simulators.
CloudSim~\cite{calheiros2011cloudsim} is a widely used event-based simulation toolkit designed for generic \gls{IaaS} Cloud Computing environments.
iCanCloud~\cite{nunez2012icancloud} similarly focuses on simulating \gls{AWS} \gls{EC2} compute infrastructure, the project's primary objectives being performance and scalability of simulations.
GreenCloud, on the other hand, is built upon the \acs{ns2}~\cite{nsnam} network simulator and specifically captures energy consumption details of datacenter components and communication patterns between these.

@@

\emph{OpenRTiST}~\cite{george2020openrtist} is a tool for the benchmarking and performance evaluation of Edge Computing deployments using real-time processing of a live video feed.
Video is streamed from a source Android device to a compute node where neural style-transfer~\cite{gatys2016image} is applied to it.
The transformed video is then fed back to the source to be presented, resulting in a compute-intensive, bandwidth-hungry, and latency-sensitive benchmark.
However, OpenRTiST is limited by its non-replaceable workload which only targets machine learning-enhanced video processing and analytics.

@@

The last few years have also seen the emergence of a number of small- to mid-scale platforms and testbeds for Edge Computing research.
Several of these are additionally driven by research interests in novel mobile networking technologies and \gls{MEC}, as well as in the virtualization of network functions.
Of particular interest to us are the
\begin{inlineenum}
    \item \acs{GENI}
    \item Chameleon
    \item \acs{COSMOS}
    \item \acs{POWDER}
    \item \acs{ARA}
    \item EdgeNet
%    \item Drexel Grid \gls{SDR}
\end{inlineenum} testbeds.

@@

Finally, a number of other, small-scale approaches also exist.
In~\cite{gedawy2016cumulus}, the authors propose Cumulus, a prototype testbed for Edge compute offloading in \gls{IOT} with the explicit goal of providing a generic and heterogeneous platform for Edge Computing research.
The authors of~\cite{rimal2018experimental} propose an experimental testbed for two-tiered Edge architectures in the context of \gls{FIWI} Edge Computing.
This testbed is then employed to validate wireless access and compute resource scheduling strategies in these systems.
In~\cite{yamanaka2021design}, the authors present an experimental Edge Computing testbed capable of determining the offload location of a workload based on desired latency parameters.
\cite{diao2019scalable} propose yet another Kubernetes-based testbed based for Edge task offloading based on heterogeneous hardware including low-power single-board computers such as Raspberry Pis and Jetson Nanos.
% \cite{moorthy2022cloudraft} proposes \gls{CLOUDRAFT}, a Cloud-based framework for mobile network experimentation, with a focus on simplifying the management of testbed resources.
% The goal of this project is to integrate, coordinate, share, and improve upon existing testbeds through a common interface.

Although the aforementioned testbeds represent valuable and powerful tools, the lack of a unified approach to testbed management and automation hinders the development and implementation of next-generation wireless systems, Cloud, and Edge computing paradigms.
General-purpose, hardware-agnostic software frameworks such as \gls{CLOUDRAFT}~\cite{moorthy2022cloudraft}  can simplify the management and automation of testbeds, promote compatibility with Cloud- and Edge-native standards, and facilitate collaboration among research groups.
\gls{CLOUDRAFT} is a Cloud-based framework for mobile network experimentation with the goal integrate, coordinate, share, and improve upon existing testbeds through a common interface.
There is still remains much work to be done in this area, particularly with respect to the adoption of Edge-compatible solutions that can enable faster and more reliable experimentation.

@@

A significant amount of work has been dedicated to the modeling and performance characterization of \glspl{NCS} due to their potential benefits for industrial and commercial settings~\cite{lu2016real,hespanha2007survey,zhang2013network,zhang2016survey}.
Research in \glspl{NCS} has mostly focused on addressing the challenges imposed by the introduction of best-effort communication networks into traditional control systems.
Network delays (latency), losses, and \emph{jitter} --- referring to the variation in random network delays --- are at the forefront of these challenges.
They have partially been addressed through the clever placement of the controller (e.g.\ by employing Edge Computing)~\cite{sasaki2017layered,sasaki2016vehicle}, as well as through the development of control algorithms capable of accounting for the effects of the network~\cite{zhang2013network}.

@@

We identify two main approaches: fully practical and partially-emulated approaches.
In a fully practical approach, the experimental setup uses real systems and hardware to test and validate the performance of the \gls{NCS}.
Examples of the application of this approach can be found in studies such as~\cite{drew2005networked,baumann2018evaluating,li2014wireless,cuenca2019periodic}.
These studies implemented wireless and microcontroller-based systems for control and validated them on a physical prototype.
In~\cite{drew2005networked}, the authors present a \gls{NCS} model which considers both random packet delay and loss on both the sensor and actuator sides of the feedback loop.
They validate their design on a physical testbed consisting of inverted pendula controlled from a central computation point over Wi-Fi.
A similar testbed is employed for validation in~\cite{baumann2018evaluating}, in which the authors develop an evaluation methodology for wireless \gls{NCS}.\@
\cite{li2014wireless} implements a wireless microcontroller-based system for vibration control and validates it on a physical prototype comprising a cantilever beam controlled using an \acs{IEEE} 802.15.4 \gls{WPAN} system.\@ \cite{cuenca2019periodic} discusses the design and implementation of a periodic event-triggered sampling and dual-rate control techniques for wireless control, and validate their contributions on a four-rotor autonomous drone platform controlled over WiFi.
\emph{NCSbench}~\cite{zoppi2020ncsbench}, an open-source \gls{NCS} benchmarking platform designed with reproducibility in mind built using the \citetitle{LEGOMindstormsEV3}~\cite{LEGOMindstormsEV3} platform, is another such example.

@@

To the best of our knowledge, there exist currently no generic, hardware-independent framework available for repeatable experimental research in Edge-bound \glspl{NCS}.
While there has been some notable work in this area, such as the work by~\cite{zoppi2020ncsbench}, existing contributions still mostly rely on proprietary and hardware that is difficult to acquire.
This limitation restricts the accessibility of the framework to researchers and practitioners, hindering the reproducibility and comparability of experimental results.
Moreover, the existing research's reliance on hardware also poses scalability limitations.
As the field of Edge Computing-enabled \glspl{NCS} continues to evolve, there is a growing demand for scalable solutions that can be easily adapted to different hardware configurations and setups.
A software-based framework that provides a flexible and scalable solution for performance evaluation of \glspl{NCS} in Edge-native contexts is currently lacking in the field.

>>>>

Nevertheless, a small body of works has attempted to tackle this challenge through analytical approaches~\cite{chen2015efficient,champati2015one,champati2016semi,al2017reliable}.
In~\cite{chen2015efficient}, the authors formulate the problem of computation offloading in \gls{MEC} as a multi-user computation offloading game, and design a distributed computation offloading algorithm that achieves a Nash equilibrium to solve it.
They demonstrate through numerical results that the proposed algorithm achieves good computation offloading performance and has good scaling capabilities.
Another work that tackles computation offloading is~\cite{champati2015one}, in which the authors propose a novel optimization algorithm for the cost optimization of hybrid clouds.
The algorithm selects tasks for remote computation on the public cloud based on their estimated processing times and the known cost of offloading them; tasks with large processing times that offset their offloading cost are offloaded.\@
\cite{champati2016semi} proposes semi-online algorithms to to minimize the time required to complete all computational tasks in a sequence, with communication delay, in Cloud Computing environments.
This is achieved by optimizing the scheduling of independent tasks with unknown processing times.
Finally, the authors of~\cite{al2017reliable} propose a model-based rate adaptation algorithm for scalable video streaming in multihop wireless networks.
The algorithm is built on a novel performance model based on stochastic network calculus and allows fast near-optimal rate adaptation for fixed transmission paths and cross-layer optimized routing.

@@

Approaches to performance evaluation of distributed systems using simulations also exist in literature, particularly geared towards the Cloud~\cite{mansouri2020cloud}.
Examples include the \emph{CloudSim}, \emph{iCanCloud}, and \emph{GreenCloud} simulators.
CloudSim~\cite{calheiros2011cloudsim} is a widely used event-based simulation toolkit designed for generic \gls{IaaS} Cloud Computing environments.
iCanCloud~\cite{nunez2012icancloud} similarly focuses on simulating \gls{AWS} \gls{EC2} compute infrastructure, the project's primary objectives being performance and scalability of simulations.
GreenCloud, on the other hand, is built upon the \acs{ns2}~\cite{nsnam} network simulator and specifically captures energy consumption details of datacenter components and communication patterns between these.

@@

\emph{OpenRTiST}~\cite{george2020openrtist} is a tool for the performance evaluation of Edge Computing deployments using real-time processing of a live video feed.
Video is streamed from a mobile device to a compute node where neural style-transfer~\cite{gatys2016image} is applied to it.
The transformed video is then fed back to the source to be presented, resulting in a compute-intensive, bandwidth-hungry, and latency-sensitive benchmark.
However, OpenRTiST is limited by its non-replaceable workload which only targets machine learning-enhanced video processing and analytics.

@@

The last few years have also seen the emergence of a number of small- to mid-scale platforms and testbeds for Edge Computing research.
Several of these are additionally driven by research interests in novel mobile networking technologies and \gls{MEC}, as well as in the virtualization of network functions.
Of particular interest to this dissertation are the
\begin{inlineenum}
    \item \acs{GENI}
    \item Chameleon
    \item \acs{COSMOS}
    \item \acs{POWDER}
    \item \acs{ARA}
    \item EdgeNet
%    \item Drexel Grid \gls{SDR}
\end{inlineenum} testbeds.

@@

Finally, a number of other, small-scale approaches also exist.
In~\cite{gedawy2016cumulus}, the authors propose Cumulus, a prototype testbed for Edge compute offloading in \gls{IOT} with the explicit goal of providing a generic and heterogeneous platform for Edge Computing research.
The authors of~\cite{rimal2018experimental} propose an experimental testbed for two-tiered Edge architectures in the context of \gls{FIWI} Edge Computing.
This testbed is then employed to validate wireless access and compute resource scheduling strategies in these systems.
In~\cite{yamanaka2021design}, the authors present an experimental Edge Computing testbed capable of determining the offload location of a workload based on desired latency parameters.
\cite{diao2019scalable} propose yet another Kubernetes-based testbed based for Edge task offloading based on heterogeneous hardware including low-power \glspl{SBC}.
% \cite{moorthy2022cloudraft} proposes \gls{CLOUDRAFT}, a Cloud-based framework for mobile network experimentation, with a focus on simplifying the management of testbed resources.
% The goal of this project is to integrate, coordinate, share, and improve upon existing testbeds through a common interface.

Although the aforementioned testbeds represent valuable and powerful tools, the lack of a unified approach to testbed management and automation hinders the development of next-generation wireless systems, Cloud, and Edge computing paradigms.
General-purpose, hardware-agnostic software frameworks such as \gls{CLOUDRAFT}~\cite{moorthy2022cloudraft}  can simplify the management and automation of testbeds, promote compatibility with Cloud- and Edge-native standards, and facilitate collaboration among research groups.
\gls{CLOUDRAFT} is a Cloud-based framework for mobile network experimentation with the goal integrate, coordinate, share, and improve upon existing testbeds through a common interface.
There is still remains much work to be done in this area, particularly with respect to the adoption of Edge-compatible solutions that can enable faster and more reliable experimentation.

@@

A significant amount of work has been dedicated to the modeling and performance characterization of \glspl{NCS} due to their potential benefits for industrial and commercial settings~\cite{lu2016real,hespanha2007survey,zhang2013network,zhang2016survey}.
Research has mostly focused on addressing the challenges imposed by the introduction of best-effort communication networks into traditional control systems.
Network delays (latency), \emph{jitter} --- the variation in random network delays ---, and losses are at the forefront of these challenges.
They have partially been addressed through the clever placement of the controller (e.g.\ by employing Edge Computing)~\cite{sasaki2017layered,sasaki2016vehicle}, as well as through the development of control algorithms capable of accounting for the effects of the network~\cite{zhang2013network}.

@@

Two main approaches can be identified: fully practical and partially-emulated approaches.
In a fully practical approach, the experimental setup uses real systems and hardware to test and validate the performance of the \gls{NCS}.
Examples of the application of this approach can be found in studies such as~\cite{drew2005networked,baumann2018evaluating,li2014wireless,cuenca2019periodic}.
These studies implemented wireless and microcontroller-based systems for control and validated them on a physical prototype.
In~\cite{drew2005networked}, the authors present a \gls{NCS} model which considers both random packet delay and loss on both the sensor and actuator sides of the feedback loop.
They validate their design on a physical testbed consisting of inverted pendula controlled from a central computation point over Wi-Fi.
A similar testbed is employed for validation in~\cite{baumann2018evaluating}, in which the authors develop an evaluation methodology for wireless \gls{NCS}.\@
\cite{li2014wireless} implements a wireless microcontroller-based system for vibration control and validates it on a physical prototype comprising a cantilever beam controlled using an \acs{IEEE} 802.15.4 \gls{WPAN} system.\@ \cite{cuenca2019periodic} discusses the design and implementation of a periodic event-triggered sampling and dual-rate control techniques for wireless control, and validate their contributions on a four-rotor autonomous drone platform controlled over WiFi.
\emph{NCSbench}~\cite{zoppi2020ncsbench}, an open-source \gls{NCS} benchmarking platform designed with reproducibility in mind built using the \citetitle{LEGOMindstormsEV3}~\cite{LEGOMindstormsEV3} platform, is another such example.

@@

To the best of my knowledge, there exist currently no generic, hardware-independent framework available for repeatable experimental research in Edge-bound \glspl{NCS}.
While there has been some notable work in this area, such as the work by~\cite{zoppi2020ncsbench}, existing contributions still mostly rely on proprietary and hardware that is difficult to acquire.
This limitation restricts the accessibility of the framework to researchers and practitioners, hindering the reproducibility and comparability of experimental results.
Moreover, existing research's reliance on hardware poses scalability limitations.
As the field of Edge Computing-enabled \glspl{NCS} continues to evolve, there is a growing demand for scalable solutions that can be easily adapted to different hardware configurations and setups.
A software-based framework that provides a flexible and scalable solution for performance evaluation of \glspl{NCS} in Edge-native contexts is currently lacking in the field.
